---
title: "Basic Plots"
date: 2019-09-10
output: github_document
---

#Github:
1. Create a GitHub repo on the Git website with an informative name
    set to “Public”, initialize with a README, and create the repo

2. Create a linked R Project using 
    File > New Project > Version Control (Git)
    Provide the repository URL (copy from GitHub)
    Assign the Project a name (usually the same as the Github repo)
    Put the Project in a reasonable place on your computer

3. Keep everything related to the analysis – data inputs, scripts, reports, output – in the same directory
4, Keep track of changes using version control (save, commit, push)


```{r setup, include = FALSE}
library(tidyverse)
```

The purpose of this file is to present a couple of basic plots using `ggplot`.

First we create a dataframe containing variables for our plots.

```{r df_create}
set.seed(1234)

plot_df = tibble(
  x = rnorm(1000, sd = .5),
  y = 1 + 2 * x + rnorm(1000)
)
```

First we show a histogram of the `x` variable.

```{r x_hist}
ggplot(plot_df, aes(x = x)) + geom_histogram()
```

Next we show a scatterplot of `y` vs `x`. 

```{r yx_scatter}
ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```


lastly, we show a histogram of the `y` variable.
```{r y_hist}
ggplot(plot_df, aes(x = y)) + geom_histogram()
```

# Section 1
##Using code chunk:

take samples from a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2
## Using inline R code.

I can take the mean of the sample, too!
The mean is `r mean(samp)`.